Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-02-26 WSSSPE1_report/WSSSPE1_summary_report.tex
use passive in sentence to avoid 'they'

The question was also posed as to whether the distinction between researcher
and developer is sensible, with James Hetherington commenting that in the UK
they have been examining a more nuanced view of research software engineers
and researcher developers. Should this be less of a contract relationship, and
more of a collaborative relationship. This is also at the core of the business
model that Kitware presented in its submission to the workshop. Are other
ingredients missing such as applied mathematicians? Should this be defined more
in terms of skill sets rather than roles and/or identities? This builds on the
comments from Vaidy Sunderam that scientists are generally good writers, and
have mathematical skills, so why can't they learn software engineering
principles?

>>>>

The question was also posed as to whether the distinction between researcher
and developer is sensible, with James Hetherington commenting that in the UK
a more nuanced view of research software engineers
and researcher developers is examined. Should this be less of a contract relationship, and
more of a collaborative relationship. This is also at the core of the business
model that Kitware presented in its submission to the workshop. Are other
ingredients missing such as applied mathematicians? Should this be defined more
in terms of skill sets rather than roles and/or identities? This builds on the
comments from Vaidy Sunderam that scientists are generally good writers, and
have mathematical skills, so why can't they learn software engineering
principles?
